Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan

### 2020-07-23 analysis/paper/paper.Rmd
update regression plot for size

```{r size-regression}
# calculate centroid size
jpgs_imported_coo_size <-
  jpgs_imported_coo %>% 
  mutate(size =  coo_centsize(jpgs_imported_coo))

# create pcs dataframe for joining
pc1_df_with_filename <-
  bind_cols(filename = rownames(pc1), pc1) %>% 
  rename(c("pc1" = "x")) %>% 
  mutate(filename = parse_number(filename))

@@

# make a dataframe for centroid size and join with pc1
jpgs_imported_coo_size_df <-
  as.data.frame(jpgs_imported_coo_size$fac) %>% 
  mutate(filename = parse_number(as.character(filename))) %>% 
  left_join(pc1_df_with_filename) %>% 
  left_join(pc2_df_with_filename)

# size boxplot by period
ggplot(jpgs_imported_coo_size_df,
       aes(size, fct_rev(phase))) +
  coord_flip() +
  geom_boxplot() +
  labs(x = "phase",
       y = "centroid size")

# build regression model
linearMod <- lm( size ~ pc1, data = jpgs_imported_coo_size_df)

ggplot(jpgs_imported_coo_size_df, 
       aes(size, pc1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~ fct_rev(phase)) +
  labs(x = "centroid size")
```

>>>>

```{r size-regression, fig.cap= "Measure "}
library(ggpubr)
library(geomorph)

jpgs_imported_coo_size <- coo_centsize(jpgs_imported_coo)
jpgs_imported_coo_size_df <- as.data.frame(jpgs_imported_coo_size) 
jpgs_imported_coo_size_df <-
  bind_cols(filename = rownames(jpgs_imported_coo_size_df), 
            jpgs_imported_coo_size_df) %>% 
  mutate(filename = parse_number(filename))

# prepare metric data for joining
pottery_data_tidy <-
  pottery_data %>%
  mutate_at(vars(starts_with(c("Thick", "Diameter"))), as.numeric) %>% 
  mutate(Height = as.numeric(Hight)) %>% 
  mutate(filename = parse_number(filename))

# prepare pcs dataframe for joining
pc1_df_with_filename <-
  bind_cols(filename = rownames(pc1), pc1) %>% 
  rename(c("pc1" = "x")) %>% 
  mutate(filename = parse_number(filename))

@@

# make a dataframe for centroid size and join with pc1
jpgs_imported_coo_size_pcs_metric <-
  jpgs_imported_coo_size_df %>% 
  mutate(filename = parse_number(as.character(filename))) %>% 
  left_join(pc1_df_with_filename) %>% 
  left_join(pc2_df_with_filename) %>% 
  left_join(pottery_data_tidy)

# size boxplot by period
boxplot_size <-
  ggplot(jpgs_imported_coo_size_pcs_metric,
         aes(Diameter1_Body, fct_rev(y))) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "body diameter (mm)", y = "") +
  scale_y_discrete(breaks = c("Pre-European", "Post-European", "Chinese"),
                   labels = c("Pre-\nEuropean", "Post-\nEuropean", "Chinese")) +
  theme(axis.text = element_text(size = 8))

# can pc1 predict size by period?
pc1_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc1",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 1.25, label.sep = "\n") +
    #stat_regline_equation(label.y = 1) +
    labs(x = "") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 1.5),
                       breaks = c(seq(0, 1, 0.5)),
                       labels = c(seq(0, 1, 0.5)))

# can pc1 predict size by period?
pc2_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc2",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 1.25, label.sep = "\n") +
    #stat_regline_equation(label.y = 1) +
    labs(x = "body diameter (mm)") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 1.5),
                       breaks = c(seq(0, 1, 0.5)),
                       labels = c(seq(0, 1, 0.5)))

# plot boxplot and regression together 
right_column <-
  plot_grid(pc1_size_reg, pc2_size_reg, ncol =1)

size_boxplot_regression <-
  plot_grid(boxplot_size,
            right_column,
            labels = c("A", "B"),
            label_size = 12,
            rel_widths = c(1.8, 3.7))

ggsave(plot = size_boxplot_regression,
       here("analysis", "figures",
            "size-boxplot-regression.jpg"),
       width = 180, 
       height = 100,
       dpi = 300,
       units = "mm")
```
